---
title: "Prediction_Neural_network"
author: "Arjun_Shine"
date: "19 October 2019"
output: html_document
---
Load the required libraries and data set
NOTE : The below given code is for predicting the strength of cement strength
So the factors for model bulding is based on that.
```{r}
library(neuralnet)

concrete<-read.csv("Input file path")
str(concrete)
```
#Normalize data

```{r}
normalize <- function(x){return((x - min(x)) / (max(x) - min(x)))}
```
#Apply normaliztion to all columns
Head and Summary of the data
```{r}
concrete_norm <- as.data.frame(lapply(concrete, normalize))
head(concrete_norm)
summary(concrete_norm)
```
#Create train and test datasets

```{r}
set.seed(123)
concrete_train <- concrete_norm[1:773,]
concrete_test <- concrete_norm[774:1030,]

names(concrete_norm)
```
#Train the model and predict

```{r}
model_concrete<-neuralnet(strength~Cement+blastfurnaceslag+fly_ash+water+superplasticizer+coarse_aggregate+fine_aggregate+age,data=concrete_train,hidden=1)
predict_hidden1<-compute(model_concrete,concrete_test[-9])
predict_hidden1$net.result
```

#plotting the model

```{r}
plot(model_concrete)
summary(model_concrete)
```


# write into a new file
```{r}
write.csv(concrete_train,"OUTPUT PATH")

```


```{r}
plot(model_concrete)
summary(model_concrete)
```

correlation 

```{r}
cor(predict_hidden1$net.result,concrete_test$strength)
```

#Model improvement

```{r}
model_concrete_improved<-neuralnet(strength~Cement+blastfurnaceslag+fly_ash+water+superplasticizer+coarse_aggregate+fine_aggregate+age,data=concrete_train,hidden=5)
plot(model_concrete_improved)
predict_hidden5<-compute(model_concrete_improved,concrete_test[-9])
cor(predict_hidden5$net.result,concrete_test$strength)
```

